\documentclass[a4paper,10.5pt]{article}

\usepackage[left=0.7in,right=0.7in,top=0.7in,bottom=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{setspace}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setstretch{1.05}

% Bullet spacing
\setlist[itemize]{itemsep=2pt, topsep=2pt, leftmargin=*}

% Section formatting with horizontal line
\titleformat{\section}
  {\bfseries\large}
  {}
  {0em}
  {}
  [\vspace{-4pt}\rule{\linewidth}{0.5pt}]

\titlespacing*{\section}{0pt}{10pt}{6pt}

\begin{document}

%================ HEADER =================
\begin{center}
{\LARGE \textbf{HIMANSHU ARORA}}\\
\vspace{4pt}
Full Stack Developer\\
\vspace{4pt}
+91 72200 00833 \quad
\href{mailto:ha344182@gmail.com}{ha344182@gmail.com} \quad
\href{https://www.linkedin.com/in/himanshuarora344182}{linkedin.com/in/himanshuarora344182}
\end{center}

%================ SUMMARY =================
\section*{PROFESSIONAL SUMMARY}

Motivated Full Stack Developer with hands-on experience building scalable and responsive e-commerce web applications. Skilled in frontend development, RESTful API creation, authentication systems, and MongoDB database integration. Strong foundation in object-oriented programming and complete application lifecycle development. Experienced in collaborative team environments with strong problem-solving ability, clear communication skills, and practical exposure to Agile development workflows.

%================ EDUCATION =================
\section*{EDUCATION}

\textbf{Bachelor of Computer Applications (BCA)} \hfill 2022 -- 2025 \\
Kamla Lohtia Sanatan Dharam College, Panjab University \\
Percentage: 75\%

\vspace{4pt}

\textbf{Higher Secondary (Class XII)} \\
BCM Arya Model Sr. Sec. School, CBSE \\
Percentage: 80\%

%================ SKILLS =================
\section*{TECHNICAL SKILLS}

\textbf{Languages:} JavaScript (ES6+), HTML5, CSS3 \\
\textbf{Frontend:} React.js, Responsive Design, Component Architecture, State Management, Axios, Tailwind CSS \\
\textbf{Backend:} Node.js, Express.js, REST APIs, JWT Authentication, Middleware, CRUD Operations, Validation \\
\textbf{Database:} MongoDB, Mongoose \\
\textbf{Core CS:} Data Structures, Algorithms, DBMS, OOP \\
\textbf{Tools:} Git, GitHub, Postman, VS Code, NPM, Render

%================ PROJECTS =================
\section*{PROJECTS}

\textbf{Zenvy E-Commerce Platform} \hfill
\href{https://zenvy.biz}{Live} \quad | \quad
\href{https://github.com/himanshu344182/zenvy-frontend}{Frontend Repo} \quad | \quad
\href{https://github.com/himanshu344182/zenvy-backend}{Backend Repo}

\begin{itemize}
\item Developed a full-stack e-commerce platform using React.js and Node.js/Express.js APIs.
\item Built responsive UI with product listing, cart management, and seamless checkout workflows.
\item Designed MongoDB schemas for users, products, carts, and integrated JWT role-based authentication.
\item Implemented comprehensive order management logic and admin product management features.
\item Applied centralized error handling, input validation middleware, and optimized state management.
\end{itemize}

\textbf{Personal Portfolio Website} \hfill
\href{https://my-portfolio-five-steel-31.vercel.app/}{Live} \quad | \quad
\href{https://github.com/himanshu344182/my-portfolio}{GitHub}

\begin{itemize}
\item Designed a responsive, modern portfolio single-page application utilizing React.js and Tailwind CSS.
\item Built dynamic components to showcase web development projects, skills, and educational background.
\item Implemented state management and performance optimizations for fast load times and clean UI.
\end{itemize}

%================ CERTIFICATIONS =================
\section*{CERTIFICATIONS}

The Fundamentals of Digital Marketing -- Google Digital Garage \\
Basics of Python -- Infosys Springboard \\
Programming using Java -- Infosys Springboard \\
Introduction to Cyber Security -- Infosys Springboard \\
Introduction to Data Science -- Infosys Springboard

\end{document}
